### 2014-11-02 evaluation.tex
edits

\begin{figure*}
  \centering
  \subfigure[Perf. Oper. 1DC]{\label{grf:LWW-perf-1DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-1DC.pdf}}
  \subfigure[Perf. Oper. 2DC]{\label{grf:LWW-perf-2DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-2DC.pdf}}
  \subfigure[Perf. Txn. 1DC]{\label{grf:LWW-txn-1DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-1DC-txn.pdf}}
  \subfigure[Mutation Prof. 1DC]{\label{grf:LWW-txn-wp}\includegraphics[width=0.24\textwidth]{graphs/LWW-txn-wp-vs-tp.pdf}}
	\caption{Performance of LWW Register RDT.}
  \label{grf:LWW_perf}
\end{figure*}

We analyze the performance of different consistency classifications in \name
using the LWW register. Our client workload was generated using YCSB
benchmark~\cite{}, with the default workload of 50\% reads and 50\% writes,
with keys uniformly chosen from a set of 1000 keys. We varied the number of
clients from 128 to 1024, with each workload running for 180 seconds.
Last-writer-wins is the conflict resolution policy used by Cassandra. Hence, we
are able to directly compare the performance of \name implementation against
Cassandra.

Figure~\ref{grf:LWW-perf-1DC} shows the throughput vs. latency graph for the
different consistency levels. We also include Cassandra, which provides basic
eventual consistency. Recall that \name's eventual consistency is stronger than
the guarantees provided by Cassandra (Section~\ref{sec:store_sem}). With 512
clients, the average latency of operations on Cassandra was 32.24 milliseconds.
EC and CC under \name was 30\% and 57\% slower whereas strong consistency was
241\% slower. EC(SC) was able to achieve 80\%(40\%) of throughput of vanilla
Cassandra. The results show that while \name provides an expressive programming
model with stronger consistency guarantees, its performance is comparable to
vanilla Cassandra. However, SC has a huge performance hit due to coordination
between all the replicas for obtaining object leases as well as reading and
writing to all replicas.

>>>>

\begin{figure*}
  \centering
  \subfigure[Operation performance 1DC]{\label{grf:LWW-perf-1DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-1DC.pdf}}
  \subfigure[Operation performance 2DC]{\label{grf:LWW-perf-2DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-2DC.pdf}}
  \subfigure[Transaction performance 1DC]{\label{grf:LWW-txn-1DC}\includegraphics[width=0.24\textwidth]{graphs/LWW-tp-vs-lat-1DC-txn.pdf}}
  \subfigure[Mutations in transactions]{\label{grf:LWW-txn-wp}\includegraphics[width=0.24\textwidth]{graphs/LWW-txn-wp-vs-tp.pdf}}
	\caption{Performance of LWW Register RDT.}
  \label{grf:LWW_perf}
\end{figure*}

We analyze the performance of different consistency classifications in \name
using the LWW register. Our client workload was generated using YCSB
benchmark~\cite{}, with the default workload of 50\% reads and 50\% writes,
with keys uniformly chosen from a set of 100,000 keys. We varied the number of
clients from 128 to 1024, with each workload running for 180 seconds.
Last-writer-wins is the conflict resolution policy used by Cassandra. Hence, we
are able to directly compare the performance of \name implementation against
Cassandra.

Figure~\ref{grf:LWW-perf-1DC} shows the throughput vs. latency graph for the
different consistency levels in \cf{1DC} configuration. We also include
Cassandra, which provides basic eventual consistency. Recall that \name's
eventual consistency is stronger than the guarantees provided by Cassandra
(Section~\ref{sec:store_sem}). With 512 clients, the average latency of
operations on Cassandra was 32.24 milliseconds. EC and CC under \name was 30\%
and 57\% slower whereas strong consistency was 241\% slower. EC(SC) was able to
achieve 80\%(40\%) of throughput of vanilla Cassandra. The results show that
while \name provides an expressive programming model with stronger consistency
guarantees, its performance is comparable to vanilla Cassandra. However, SC has
a huge performance hit due to coordination between all the replicas for
obtaining object leases as well as reading and writing to all replicas. This
overhead worsens in a WAN setting. Figure~\ref{grf:LWW-perf-2DC} shows the
throughput vs. latency graph under 2DC configuration. While the Cassandra, EC
and CC numbers largely remain the same when compared to 1DC configuration, SC
is 6$\times$ to 12$\times$ higher latency and lower throughput than than the
1DC case.

We compare the performance of different transaction isolation level choices in
Figure~\ref{grf:LWW-txn-1DC}. The numbers were obtained under 1DC
configuration. The YCSB workload was modified to issue 10 operations per
transaction. Each operation is assumed to have eventual consistency. \cf{NoTxn}
corresponds to a configuration that does not use transactions. Compared to this
RC is only 12\% shower in terms of latency with 512 clients, where as RR is
2.3X slower. The difference between RC and \cf{NoTxn} is due to the meta-data
overhead of recording transaction information in the object state. For RR
transaction, The cost of capturing and maintaining the snapshot in an RR
transaction is the biggest source of overhead.

Moreover, the size of the snapshot is proportional to the the number of
different objects accessed by the session as well as the number of updates.
Hence, with increasing proportion of writes, the overhead of RR transaction
increases as shown in Figure~\ref{grf:LWW-txn-wp}. The numbers were obtained
with 128 clients. Compared to an RC transaction whose throughput decreasess
45\% as the write proportion increases from 0\% to 50\%, RR transaction's
throughput drops 78\% in the same interval.
